Practical Optional Types for Clojure

### 2015-02-27 overview.tex
overview

\clj{inc-map} is like example~\ref{example:decmap} except the nodes are incremented.
The reasoning is similar, except we only use positive
information since we only consider the \emph{dispatch value} and how it relates
to the \emph{dispatch function}.
In the \clj{:do} method we learn the \clj{:op} key is a \clj{:do}, which
narrows our argument type to the \clj{:do} Expr, and similarly for the \clj{:if}
and \clj{:const} methods.

>>>>

\clj{inc-map} is like example~\ref{example:decmap} except the nodes are incremented.
The reasoning is similar, except we only consider one branch (the current method) by
locally considering the current \emph{dispatch value} and reasoning about how it relates
to the \emph{dispatch function}.
For example, 
in the \clj{:do} method we learn the \clj{:op} key is a \clj{:do}, which
narrows our argument type to the \clj{:do} Expr, and similarly for the \clj{:if}
and \clj{:const} methods.
